### 2021-10-22 paper.Rmd
typo

In a next step, I compared k-means anticlustering, k-plus anticlustering and anticluster editing in their ability to equalize means and standard deviations between groups. To clarify the general pattern of results, Table 1 illustrates the outcome variables  $\Delta M$ and $\Delta \mathit{SD}$ after splitting the sample size into categories and averaging across simulation runs. Note that the results have also been collapsed across the different group sizes ($K = 2, 3, 4$) because the relative performance of the anticlustering methods did not vary by $K$.[^kmaineffect] Table 1 shows that k-means was best suited to equalize mean values between groups; this advantage was most pronounced for smaller samples sizes. For larger sample sizes, k-plus anticlustering and anticluster editing performed similarly well with regard to $\Delta M$. Replicating @papenberg2020, it is shown that anticluster editing better minimizes differences with regard to standard deviations between groups than k-means anticlustering. Noteworthy, however, k-plus anticlustering strongly outperformed both competitors in this matter; $\Delta \mathit{SD}$ was consistently lowest for the new k-plus method. In conclusion, k-plus anticlustering is well suited to minimize differences with regard to mean values across groups---especially when groups are larger---and at the same time is able to minimize differences in standard deviations between groups.

>>>>

In a next step, I compared k-means anticlustering, k-plus anticlustering and anticluster editing in their ability to equalize means and standard deviations between groups. To clarify the general pattern of results, Table 1 illustrates the outcome variables  $\Delta M$ and $\Delta \mathit{SD}$ after splitting the sample size into categories and averaging across simulation runs. Note that the results have also been collapsed across the different group sizes ($K = 2, 3, 4$) because the relative performance of the anticlustering methods did not vary by $K$.[^kmaineffect] Table 1 shows that k-means was best suited to equalize mean values between groups; this advantage was most pronounced for smaller group sizes. For larger group sizes, k-plus anticlustering and anticluster editing performed similarly well with regard to $\Delta M$. Replicating @papenberg2020, it is shown that anticluster editing better minimizes differences with regard to standard deviations between groups than k-means anticlustering. Noteworthy, however, k-plus anticlustering strongly outperformed both competitors in this matter; $\Delta \mathit{SD}$ was consistently lowest for the new k-plus method. In conclusion, k-plus anticlustering is well suited to minimize differences with regard to mean values across groups---especially when groups are larger---and at the same time is able to minimize differences in standard deviations between groups.
